Regularising Lotka--Volterra interaction matrices by species grouping: optimal groupings are unpredictable

### 2022-03-19 article.rnw
Correct the comparator in an inequality.
The sentence previously stated that *over* 100 parameters
were required for a model of 10 species.
08b69117c28ed648a444812afb75dcaaeb6d4db4 changed the wording to
"*the interactions in* a model of 10 species",
so that the inequality should state *at least* 100 parameters required.

Making practical use of a model requires experimentally or observationally determining the values of each of the model's parameters.
This poses a particular problem for models that include species interactions due to the sheer number of parameters that must be determined.
Even the simplest models with no environmental dependence require one parameter to characterize the interaction of each pair of species \parencite{novak2016characterizing, XXX}.
Hence the number of parameters scales quadratically with the number of species; over \num{100} parameters are required for the interactions in a community of ``just'' \num{10} species.
Determining these parameters experimentally requires at least one experiment per parameter, and preferably more \parencite{hart2018quantify}.
This is expensive, and requires a lot of effort.
As such, model-based predictions of real communities are typically restricted to a small number of focal species \parencite{ovaskainen2017species, XXX}.
However, real communities can contain hundreds of species \parencite{cornell1999unsaturation}, or even thousands for microbial communities assessed by genetic metabarcoding \parencite{warton2015variables}.
To bridge this gap between XXX and YYY, we need an ecologically-defensible way to reduce the number of parameters that predictive models require.

>>>>

Making practical use of a model requires experimentally or observationally determining the values of each of the model's parameters.
This poses a particular problem for models that include species interactions due to the sheer number of parameters that must be determined.
Even the simplest models with no environmental dependence require one parameter to characterize the interaction of each pair of species \parencite{novak2016characterizing, XXX}.
Hence the number of parameters scales quadratically with the number of species; at least \num{100} parameters are required for the interactions in a community of ``just'' \num{10} species.
Determining these parameters experimentally requires at least one experiment per parameter, and preferably more \parencite{hart2018quantify}.
This is expensive, and requires a lot of effort.
As such, model-based predictions of real communities are typically restricted to a small number of focal species \parencite{ovaskainen2017species, XXX}.
However, real communities can contain hundreds of species \parencite{cornell1999unsaturation}, or even thousands for microbial communities assessed by genetic metabarcoding \parencite{warton2015variables}.
To bridge this gap between XXX and YYY, we need an ecologically-defensible way to reduce the number of parameters that predictive models require.
